---
format: gfm
---
```{r setup, include=FALSE}
project <- yaml::read_yaml("_viash.yaml")
license <- paste0(project$links$repository, "/blob/main/LICENSE")
contributing <- paste0(project$links$repository, "/blob/main/CONTRIBUTING.md")
```
# 🌱📦 `r project$name`

[![ViashHub](https://img.shields.io/badge/ViashHub-`r project$name`-7a4baa)](https://www.viash-hub.com/packages/`r project$name`) 
[![GitHub](https://img.shields.io/badge/GitHub-viash--hub%2F`r project$name`-blue)](`r project$links$repository`) 
[![GitHub License](https://img.shields.io/github/license/viash-hub/`r project$name`)](`r license`) 
[![GitHub Issues](https://img.shields.io/github/issues/viash-hub/`r project$name`)](`r project$links$issue_tracker`) 
[![Viash version](https://img.shields.io/badge/Viash-v`r gsub("-", "--", project$viash_version)`-blue)](https://viash.io)

`r project$summary`

## Introduction

`r project$description`

## Example Usage

### 1. Via the Viash Hub Launch interface

...

### 2. Via the Viash CLI

...

### 3. Via the Nextflow CLI

...

### 4. As a dependency

...

## Contributing

Contributions are welcome! We aim to build a comprehensive collection of high-quality bioinformatics components. If you'd like to contribute, please follow these general steps:


```{r echo=FALSE}
lines <- readr::read_lines("CONTRIBUTING.md")

index_start <- grep("^### Step [0-9]*:", lines)

index_end <- c(index_start[-1] - 1, length(lines))

name <- gsub("^### Step [0-9]*: *", "", lines[index_start])

knitr::asis_output(
  paste(paste0(" 1. ", name, "\n"), collapse = "")
)
```

See the [CONTRIBUTING](`r contributing`) file for more details.

