---
format: gfm
---
```{r setup, include=FALSE}
project <- yaml::read_yaml("_viash.yaml")
license <- paste0(project$links$repository, "/blob/main/LICENSE")
contributing <- paste0(project$links$repository, "/blob/main/CONTRIBUTING.md")
```
# 🌱📦 `r project$name`

[![ViashHub](https://img.shields.io/badge/ViashHub-`r project$name`-7a4baa)](https://web.viash-hub.com/packages/`r project$name`) 
[![GitHub](https://img.shields.io/badge/GitHub-viash--hub%2F`r project$name`-blue)](`r project$links$repository`) 
[![GitHub License](https://img.shields.io/github/license/viash-hub/`r project$name`)](`r license`) 
[![GitHub Issues](https://img.shields.io/github/issues/viash-hub/`r project$name`)](`r project$links$issue_tracker`) 
[![Viash version](https://img.shields.io/badge/Viash-v`r gsub("-", "--", project$viash_version)`-blue)](https://viash.io)

`r project$description`

## Objectives

- **Reusability**: Facilitating the use of components across various projects and contexts.
- **Reproducibility**: Ensuring that components are reproducible and can be easily shared.
- **Best Practices**: Adhering to established standards in software development and bioinformatics.

## Contributing

We encourage contributions from the community. To contribute:

1. **Fork the Repository**: Start by forking this repository to your account.
2. **Develop Your Component**: Create your Viash component, ensuring it aligns with our best practices (detailed below).
3. **Submit a Pull Request**: After testing your component, submit a pull request for review.

## Contribution Guidelines

The contribution guidelines describes which steps you should follow to contribute a component to this repository.

```{r echo=FALSE}
lines <- readr::read_lines("CONTRIBUTING.md")

index_start <- grep("^### Step [0-9]*:", lines)

index_end <- c(index_start[-1] - 1, length(lines))

name <- gsub("^### Step [0-9]*: *", "", lines[index_start])

knitr::asis_output(
  paste(paste0(" 1. ", name, "\n"), collapse = "")
)
```

See the [CONTRIBUTING](`r contributing`) file for more details.


## Support and Community

For support, questions, or to join our community:

- **Issues**: Submit questions or issues via the [GitHub issue tracker](`r project$links$issue_tracker`).
- **Discussions**: Join our discussions via [GitHub Discussions](`r project$links$repository`/discussions).

## License
This repository is licensed under an MIT license. See the [LICENSE](`r license`) file for details.
