---
format: gfm
---
```{r setup, include=FALSE}
package <- yaml::read_yaml("_viash.yaml")
license <- paste0(package$links$repository, "/blob/main/LICENSE")
contributing <- paste0(package$links$repository, "/blob/main/CONTRIBUTING.md")

pkg <- package$name
ver <- if (!is.null(package$version)) package$version else "v0.4.0"
comp <- "bowtie2_align"

# Count components
component_dirs <- list.dirs("src", recursive = FALSE, full.names = FALSE)
component_dirs <- component_dirs[!startsWith(component_dirs, "_")]
n_tools <- length(component_dirs)
```

# 🌱📦 `r pkg`

[![ViashHub](https://img.shields.io/badge/ViashHub-`r pkg`-7a4baa.svg)](https://www.viash-hub.com/packages/`r pkg`) 
[![GitHub](https://img.shields.io/badge/GitHub-viash--hub%2F`r pkg`-blue.svg)](`r package$links$repository`) 
[![GitHub License](https://img.shields.io/github/license/viash-hub/`r pkg`.svg)](`r license`) 
[![GitHub Issues](https://img.shields.io/github/issues/viash-hub/`r pkg`.svg)](`r package$links$issue_tracker`) 
[![Viash version](https://img.shields.io/badge/Viash-v`r gsub("-", "--", package$viash_version)`-blue.svg)](https://viash.io)

**A curated collection of high-quality, production-ready bioinformatics components**

Built with [Viash](https://viash.io), `r pkg` provides reliable, containerized tools for genomics and bioinformatics workflows. Each component is thoroughly tested, fully documented, and designed for seamless integration into both standalone and Nextflow pipelines.

## Why Choose `r pkg`?

✅ **Production Ready**: All components are containerized with pinned versions and comprehensive testing  
✅ **Nextflow Native**: Drop-in compatibility with Nextflow workflows  
✅ **Complete Documentation**: Full parameter exposure with detailed help and examples  
✅ **Quality Assured**: Unit tested with automated CI/CD validation  
✅ **Modern Standards**: Built with current best practices and maintained dependencies  

## Featured Tools

Our collection spans the complete bioinformatics pipeline:

**Alignment & Mapping**: BWA, Bowtie2, STAR, Kallisto, Salmon  
**Quality Control**: FastQC, Falco, MultiQC, Qualimap, NanoPlot  
**Preprocessing**: Cutadapt, fastp, Trimgalore, UMI-tools  
**Variant Calling**: BCFtools, LoFreq, SnpEff  
**File Manipulation**: SAMtools, Bedtools, seqtk  
**Assembly & Annotation**: BUSCO, AGAT, GFFread  
**Single Cell**: CellRanger, BD Rhapsody  

[View all components →](https://www.viash-hub.com/packages/`r pkg`)

## Quick Start

You can run Viash components from `r pkg` in several ways:

**🌐 Via Viash Hub Web UI**: Interactive interface with documentation and examples  
**⚡ As Standalone Executables**: Direct command-line execution  
**🔄 Via Nextflow**: Local or cloud-based pipeline workflows  

For detailed instructions on each method, visit the **[Viash Hub documentation →](https://viash-hub.com/packages/`r pkg`)** where each component page shows exactly how to run it in different environments.

```{r mmd, echo=FALSE, results='asis'}
cat(
  "```mermaid\n",
  "flowchart LR\n",
  "    A[", pkg, " Components] --> B[🌐 Web UI]\n",
  "    A --> C[⚡ Standalone]\n",
  "    A --> D[🔄 Nextflow Local]\n",
  "    A --> E[☁️ Nextflow Cloud]\n",
  "    \n",
  "    style A fill:#7a4baa,color:#fff\n",
  "    style B fill:#e1f5fe,color:#000\n",
  "    style C fill:#e8f5e8,color:#000\n",
  "    style D fill:#fff3e0,color:#000\n",
  "    style E fill:#f3e5f5,color:#000\n",
  "```\n",
  sep = ""
)
```

You can run components directly from Viash Hub's launch interface. See [Viash Hub](https://www.viash-hub.com/packages/`r pkg`) for more information.


## Contributing

We welcome contributions! `r pkg` thrives on community input to expand our collection of high-quality bioinformatics components.

### Quick Contribution Process

1. **Fork** the repository
2. **Create** your component following our guidelines  
3. **Test** thoroughly with `viash test`
4. **Submit** a pull request

### What We're Looking For

- **Popular bioinformatics tools** missing from our collection
- **Improvements** to existing components
- **Bug fixes** and documentation enhancements
- **Best practice** implementations

### Getting Started

Check out our comprehensive guides:

- **[Contributing Guidelines](`r contributing`)** - Complete development guide
- **[Component Standards](docs/COMPONENT_DEVELOPMENT.md)** - Quality requirements
- **[Testing Guide](docs/TESTING.md)** - Validation best practices

**New to Viash?** Start with our [beginner-friendly issues](https://github.com/viash-hub/biobox/labels/good%20first%20issue) or join our [community discussions](https://github.com/viash-hub/biobox/discussions).

## Community & Support

- **Documentation**: [Viash Documentation](https://viash.io)
- **Discussions**: [GitHub Discussions](https://github.com/viash-hub/biobox/discussions)
- **Issues**: [Bug Reports & Feature Requests](https://github.com/viash-hub/biobox/issues)

---

**Ready to streamline your bioinformatics workflows?** [Get started with `r pkg` today →](https://www.viash-hub.com/packages/`r pkg`)
